Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-11 latex/comp_or.tex
New table for processes performance

\newcommand{\Comentar}[1]{\State {\cmmt{#1}}}
\newcommand{\Break}{\State \textbf{break}}
\renewcommand{\Return}{\State \textbf{return}~}
\renewcommand{\algorithmicensure}{\textbf{Parameters:}}

@@

\begin{table}[H]
	\centering
	\caption{Smaller aircraft parameters}  \label{tab:smaller}
	\footnotesize
	\begin{tabular}{c | c c c c c c c}
		\toprule
		\textbf{Limits}  & \multicolumn{3}{c}{$Payload$: $26,000kg$} & \multicolumn{4}{c}{$limit^{CG}_{long}$: $0.556m$} \\
		\midrule
		\bf{Pallets} & $p_7$ & $p_6$ & $p_5$ & $p_4$ & $p_3$ & $p_2$ & $p_1$ \\
		\midrule
		{\bf CGx ($m$)}     & -5.10 & -2.70 & -0.30   & 2.10 & 4.50 & 6.25 & 8.39  \\
		\midrule
		{\bf Weight limits ($kg$)}  & 4,500  &  4,500 &  4,500   & 4,500 & 4,500 & 4,000 & 3,500 \\ 
		{\bf Volume limits ($m^3$)} & 13.7  &  13.7 &  13.7   & 13.7 & 13.7 & 8.9 & 6.9 \\ 
		\midrule

		\textbf{Costs}  & \multicolumn{4}{c}{$c_d$: US\$ $1.100/km$ } &	\multicolumn{3}{c}{$c_g = 0.05$} \\

@@

\begin{table}[H]
	\centering
	\caption{Larger aircraft parameters}  \label{tab:larger}
	\footnotesize
	\begin{tabular}{c | c c c c c c c c c}
		\toprule
		\textbf{Limits}& \multicolumn{3}{c}{$Payload$: $75,000kg$} & \multicolumn{3}{c}{$limit^{CG}_{long}$: $1.170m$} &
		\multicolumn{3}{c}{$limit^{CG}_{lat}$: $0.19m$} \\
		\midrule
		\multirow{2}{*}{\textbf{Pallets}}  & $p_{17}$ & $p_{15}$ & $p_{13}$ & $p_{11}$ & $p_{9}$ & $p_{7}$ & $p_{5}$ & $p_{3}$ & $p_{1}$ \\
		& $p_{18}$ & $p_{16}$ & $p_{14}$ & $p_{12}$ & $p_{10}$ & $p_{8}$ & $p_{6}$ & $p_{4}$ & $p_{2}$ \\
		\midrule 
		\multirow{2}{*}{\textbf{CGx ($m$)}} & -17.57 & -13.17 & -8.77 & -4.40 & 0 & 4.40 & 8.77 & 11.47 & 14.89 \\
		& -17.57 & -13.17 & -8.77 & -4.40 & 0 & 4.40 & 8.77 & 11.47 & 14.89 \\			
		\midrule 
		\multirow{2}{*}{\textbf{CGy ($m$)}}  & 1.32 & 1.32 & 1.32 & 1.32 & 1.32 & 1.32 & 1.32 & 1.32 & 1.32 \\
		& -1.32 & -1.32 & -1.32 & -1.32 & -1.32 & -1.32 & -1.32 & -1.32 & -1.32 \\	
		\midrule
		{\bf Weight limits ($kg$)}      &   4,500   &    4,500  &   4,500   &  4,500    & 4,500     & 4,500     & 4,500     & 4,000    & 3,000   \\
		{\bf Volume limits ($m^3$)}   &   14.8   &   14.8   &  14.8    &  14.8    & 14.8     & 14.8     & 14.8     & 10.0    & 7.0 \\	
		\midrule

		\textbf{Costs}  & \multicolumn{5}{c}{ $c_d$: US\$ $4.900/km$ } &	\multicolumn{4}{c}{$c_g = 0.05$} \\

@@

For parallelization, we used the {\it Python multiprocessing} package, which implements {\it process-based parallelism or parallel shared memory algorithm}. According to \cite{multiprocessing}, Multiprocessing is a package that supports spawning processes using an API similar to the threading module.

The multiprocessing package offers both local and remote concurrency, effectively side-stepping the global interpreter lock by using sub-processes instead of threads. Because of this, the multiprocessing module lets the programmer take full advantage of the fact that a machine has more than one processor. This decision for multiprocessing relies on the need to exchange information among processes, which would be harder to handle with thread-based parallelism.

@@

\begin{table}[H]
	\centering
	\caption{Methods and scenarios with $volume=1.2$}  \label{tab:20}
	\footnotesize
	\begin{tabular}{l|c|cccccc|c}
		\toprule
		{$method$}                        &{\bf Results}    &{\bf 1}     &{\bf 2}    &{\bf 3}      &{\bf 4}      &{\bf 5}      &{\bf 6}     &\specialcell{{\bf Normalized}\\{\bf Speed-up}} \\
		\toprule

		\multirow{2}{*}{\textbf{Shims}}   & $f$              & 5.40        & 2.94        &          &          &          &         &   \\ 
		                                  &{\bf run-time (s)}& <1          & 1           &             &            &            &          &   \\ %206s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{Shims-p}} & $f$              & 5.88        & 3.16        &          &          &          &         &   \\ 
		                                  &{\bf run-time (s)}& 1           & 10          &             &            &            &          &   \\ %299s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{ACO}}     & $f$              & 5.77        &         &          &        &       &      &   \\ 
                                          &{\bf run-time (s)}& 14          &          &           &        &       &      &   \\ 
        \midrule[.1pt]

        \multirow{2}{*}{\textbf{ACO-p}}   & $f$              & 5.82        &         &          &         &       &       &   \\ 
                                          &{\bf run-time (s)}& 22          &           &           &         &       &       &   \\

>>>>

\newcommand{\Comentar}[1]{\State {\cmmt{#1}}}
\newcommand{\Break}{\State \bf {break}}
\renewcommand{\Return}{\State \bf {return}~}
\renewcommand{\algorithmicensure}{\bf {Parameters:}}

@@

\begin{table}[H]
	\centering
	\caption{Smaller aircraft parameters}  \label{tab:smaller}
	\footnotesize
	\begin{tabular}{c | c c c c c c c}
		\toprule
		\bf {Limits}  & \multicolumn{3}{c}{$Payload$: $26,000kg$} & \multicolumn{4}{c}{$limit^{CG}_{long}$: $0.556m$} \\
		\midrule
		\bf {Pallets} & $p_7$ & $p_6$ & $p_5$ & $p_4$ & $p_3$ & $p_2$ & $p_1$ \\
		\midrule
		{\bf CGx ($m$)}     & -5.10 & -2.70 & -0.30   & 2.10 & 4.50 & 6.25 & 8.39  \\
		\midrule
		{\bf Weight limits ($kg$)}  & 4,500  &  4,500 &  4,500   & 4,500 & 4,500 & 4,000 & 3,500 \\ 
		{\bf Volume limits ($m^3$)} & 13.7  &  13.7 &  13.7   & 13.7 & 13.7 & 8.9 & 6.9 \\ 
		\midrule

		\bf {Costs}  & \multicolumn{4}{c}{$c_d$: US\$ $1.100/km$ } &	\multicolumn{3}{c}{$c_g = 0.05$} \\

@@

\begin{table}[H]
	\centering
	\caption{Larger aircraft parameters}  \label{tab:larger}
	\footnotesize
	\begin{tabular}{c | c c c c c c c c c}
		\toprule
		\bf {Limits}& \multicolumn{3}{c}{$Payload$: $75,000kg$} & \multicolumn{3}{c}{$limit^{CG}_{long}$: $1.170m$} &
		\multicolumn{3}{c}{$limit^{CG}_{lat}$: $0.19m$} \\
		\midrule
		\multirow{2}{*}{\bf {Pallets}}  & $p_{17}$ & $p_{15}$ & $p_{13}$ & $p_{11}$ & $p_{9}$ & $p_{7}$ & $p_{5}$ & $p_{3}$ & $p_{1}$ \\
		& $p_{18}$ & $p_{16}$ & $p_{14}$ & $p_{12}$ & $p_{10}$ & $p_{8}$ & $p_{6}$ & $p_{4}$ & $p_{2}$ \\
		\midrule 
		\multirow{2}{*}{\bf {CGx ($m$)}} & -17.57 & -13.17 & -8.77 & -4.40 & 0 & 4.40 & 8.77 & 11.47 & 14.89 \\
		& -17.57 & -13.17 & -8.77 & -4.40 & 0 & 4.40 & 8.77 & 11.47 & 14.89 \\			
		\midrule 
		\multirow{2}{*}{\bf {CGy ($m$)}}  & 1.32 & 1.32 & 1.32 & 1.32 & 1.32 & 1.32 & 1.32 & 1.32 & 1.32 \\
		& -1.32 & -1.32 & -1.32 & -1.32 & -1.32 & -1.32 & -1.32 & -1.32 & -1.32 \\	
		\midrule
		{\bf Weight limits ($kg$)}      &   4,500   &    4,500  &   4,500   &  4,500    & 4,500     & 4,500     & 4,500     & 4,000    & 3,000   \\
		{\bf Volume limits ($m^3$)}   &   14.8   &   14.8   &  14.8    &  14.8    & 14.8     & 14.8     & 14.8     & 10.0    & 7.0 \\	
		\midrule

		\bf {Costs}  & \multicolumn{5}{c}{ $c_d$: US\$ $4.900/km$ } &	\multicolumn{4}{c}{$c_g = 0.05$} \\

@@

For parallelization, we used the {\it Python multiprocessing} package, which implements {\it process-based parallelism} or {\it parallel shared memory algorithm}. According to \cite{multiprocessing}, {\it Multiprocessing} is a package that supports spawning processes using an API similar to the {\it Python Threading} package.

The {\it Multiprocessing} package (mp) offers both local and remote concurrency, effectively side-stepping the global interpreter lock by using sub-processes instead of threads. Because of this, the {\it Multiprocessing} module lets the programmer take full advantage of the fact that a machine has more than one processor, 48 in our computer. This decision for {\it Multiprocessing} relies on the need to exchange information among processes (the pheromone trails or some information regarding load balancing, in our case), which would be harder to handle with thread-based parallelism.

@@

\begin{table}[H]
	\centering
	\caption{Performance for different number of concurrent processes with $1.2 \times volume$}  \label{tab:procs}
%	\footnotesize
	\scriptsize
	\begin{tabular}{c| c | c | c c c c c c }
	\toprule
	\textbf{Scenario} & $method$ &{\bf Results}     & \textbf{1} & \textbf{4} & \textbf{8} & \textbf{16} & \textbf{24} & \textbf{32}  \\
	\toprule
	\multirow{4}{*}{\bf {1}}  &\multirow{2}{*}{\it {mpShims}}  &$f$               & 1 & 4 & 8 & 16 & 24 & 32 \\
	                          &                                &{\bf run-time (s)}& 1 & 4 & 8 & 16 & 24 & 32 \\
                              \cmidrule{2-9}
	                          &\multirow{2}{*}{\it {mpACO}}    &$f$               & 1 & 4 & 8 & 16 & 24 & 32 \\
	                          &                                &{\bf run-time (s)}& 1 & 4 & 8 & 16 & 24 & 32 \\
	\cmidrule{1-9}
	\multirow{4}{*}{\bf {2}}  &\multirow{2}{*}{\it {mpShims}} &$f$               & 1 & 4 & 8 & 16 & 24 & 32 \\
	                          &   &{\bf run-time (s)}& 1 & 4 & 8 & 16 & 24 & 32 \\
                              \cmidrule{2-9}
	                          &\multirow{2}{*}{\it {mpACO}}   &$f$               & 1 & 4 & 8 & 16 & 24 & 32 \\
	                          &   &{\bf run-time (s)}& 1 & 4 & 8 & 16 & 24 & 32 \\				
	\bottomrule		
\end{tabular}

\begin{table}[H]
	\centering
	\caption{Methods and scenarios with $1.2 \times volume$}  \label{tab:20}
%	\footnotesize
\scriptsize
	\begin{tabular}{r|c|c|cccccc|c}
		\toprule
		{$method$}                     &{\bf Procs}              &{\bf Results}     &{\bf 1}     &{\bf 2}    &{\bf 3}      &{\bf 4}      &{\bf 5}      &{\bf 6}     &\specialcell{{\bf Normalized}\\{\bf Speed-up}} \\
		\toprule

		\multirow{2}{*}{\it {Shims}}   &\multirow{2}{*}{\bf {1}} & $f$              & 5.40        & 2.94    & 2.93         &          &          &         &   \\ 
		                               &                         &{\bf run-time (s)}& <1          & 1       & 4            &            &            &          &   \\ %206s
		\midrule[.1pt]

		\multirow{2}{*}{\it {mpShims}} &\multirow{2}{*}{\bf {24}}& $f$              & 5.88        & 3.16    & 3.16         &          &          &         &   \\ 
		                               &                         &{\bf run-time (s)}& 1           & 10      & 41           &            &            &          &   \\ %299s
		\midrule[.1pt]

		\multirow{2}{*}{\it {ACO}}     &\multirow{2}{*}{\bf {1}} & $f$              & 5.77        & 3.49    &          &        &       &      &   \\ 
                                       &                         &{\bf run-time (s)}& 14          & 808     &           &        &       &      &   \\ 
        \midrule[.1pt]

        \multirow{2}{*}{\it {mpACO}}   &\multirow{2}{*}{\bf {32}}& $f$              & 5.82        & 3.12    &          &         &       &       &   \\ 
                                       &                         &{\bf run-time (s)}& 22          & 473     &           &         &       &       &   \\
